Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-06 paper.tex
Funding section

% Franz
\affil[1]{Cluster of Excellence ``Controlling Microbes to Fight Infections'', Mathematical and Computational Population Genetics, University of T\"ubingen}
% Gertjan, Konrad
\affil[2]{Institute of Evolutionary Biology, The University of Edinburgh}
% Daniel
\affil[3]{Khoury College of Computer Sciences, Northeastern University}
% Graham
\affil[4]{Lundbeck GeoGenetics Centre, Globe Institute, University of Copenhagen}
% Aaron
\affil[5]{Department of Integrative Biology, University of Wisconsin--Madison}
% Georgia
\affil[6]{Melbourne Integrative Genomics, School of Mathematics and Statistics,
    University of Melbourne}
% Jerome, Yan, Wilder, Joe
\affil[7]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford}

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{Fresh Pond Research Institute}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology, University of Oregon}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research
Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill}
\affil[13]{Embark Veterinary, Inc., Boston}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute}
% Michael
\affil[17]{Natural History Museum, University of Oslo}
% Simon, Dom, Ivan
\affil[18]{Department of Human Genetics, McGill University}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California Irvine}
% Hugo
\affil[24]{No affiliation}
% Wilder 2
\affil[25]{Broad Institute of MIT and Harvard}
% Jere
\affil[26]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[27]{Department of Mathematics, University of Oregon}

@@

\section*{Acknowledgments}
We acknowledge the contributions of Ivan Krukov who we consider
eligible for authorship, but were unable to contact for approval.
We would like to thank Iain Mathieson and Alywyn Scally for helpful comments
on the manuscript.
% alphabetised by author. Names spelled out if there's an initial collision
ADK was supported by NIH awards R01GM117241 and R01HG010774.
BE was supported by  DFG grant  273887127 through Priority Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
FB is funded by the Deutsche Forschungsgemeinschaft EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
GB and KL are supported by an ERC starting grant (ModelGenomLand 757648) to KL.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Gregor Gorjanc is supported by the Chancellor's Fellowship of the University of Edinburgh and the BBSRC grant to The Roslin Institute BBS/E/D/30002275.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
Jerome Kelleher is supported by the Robertson Foundation.
SG acknowledges funding from the Canada Research Chairs Program, from the Canadian Institutes of Health Research PJT 173300, and from the Canadian Foundation for Innovation.

>>>>

% Franz
\affil[1]{Cluster of Excellence ``Controlling Microbes to Fight Infections'', Mathematical and Computational Population Genetics, University of T\"ubingen, 72076 T\"ubingen, Germany}
% Gertjan, Konrad
\affil[2]{Institute of Evolutionary Biology, The University of Edinburgh, EH9 3FL, UK}
% Daniel
\affil[3]{Khoury College of Computer Sciences, Northeastern University, MA 02115, USA}
% Graham
\affil[4]{Lundbeck GeoGenetics Centre, Globe Institute, University of Copenhagen, 1350 Copenhagen K, Denmark}
% Aaron
\affil[5]{Department of Integrative Biology, University of Wisconsin--Madison, WI 53706, USA}
% Georgia
\affil[6]{Melbourne Integrative Genomics, School of Mathematics and Statistics, University of Melbourne, Victoria, 3010, Australia}
% Jerome, Yan, Wilder, Joe
\affil[7]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, University of Oxford, OX3 7LF, UK}

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin, 10115, Germany }
% Castedo
\affil[9]{Fresh Pond Research Institute, Cambridge, MA 02140, USA}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology, University of Oregon, OR 97405, USA}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill, NC 27599-7264, USA}
\affil[13]{Embark Veterinary, Inc., Boston, MA 02111, USA}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD, 21201, USA}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute, 141 83 Huddinge, Sweden}
% Michael
\affil[17]{Natural History Museum, University of Oslo, Blindern 0318 Oslo, Norway}
% Simon, Dom, Ivan
\affil[18]{Department of Human Genetics, McGill University, Montr\'eal, QC H3A 0C7, Canada}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University, PA 16802, USA}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, Powai, Mumbai 400 076, Maharashtra, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich, 85354 Freising, Germany}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California, Irvine, CA 92697, USA}
% Hugo
\affil[24]{No affiliation}
% Wilder 2
\affil[25]{Broad Institute of MIT and Harvard, Cambridge, MA 02142, USA}
% Jere
\affil[26]{Department of Statistics, University of Warwick, CV4 7AL, UK}
% Peter (second affil)
\affil[27]{Department of Mathematics, University of Oregon, OR 97405 USA}

@@

\section*{Acknowledgments}
We acknowledge the contributions of Ivan Krukov who we consider
eligible for authorship, but were unable to contact for approval.
We would like to thank Iain Mathieson and Alywyn Scally for helpful comments
on the manuscript.

\section*{Funding}
% alphabetised by author. Names spelled out if there's an initial collision
ADK was supported by NIH awards R01GM117241 and R01HG010774.
BE was supported by  DFG grant  273887127 through Priority Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
FB is funded by the Deutsche Forschungsgemeinschaft EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
GB and KL are supported by an ERC starting grant (ModelGenomLand 757648) to KL.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Gregor Gorjanc is supported by the Chancellor's Fellowship of the University of Edinburgh and the BBSRC grant to The Roslin Institute BBS/E/D/30002275.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
Jerome Kelleher is supported by the Robertson Foundation.
SG acknowledges funding from the Canada Research Chairs Program, from the Canadian Institutes of Health Research PJT 173300, and from the Canadian Foundation for Innovation.
